### 2017-06-29 paper.tex
Fixing wording

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education \cite{browning2012},
this knowledge and expertise is rarely transferred into classroom practice.

>>>>

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since a large number of college and university faculty have little or no training in education \cite{browning2012},
this knowledge and expertise is rarely transferred into classroom practice.
